Clarifying Correlation and Causation: A Guide to Modern Quantitative Causal Inference in Nonprofit Studies

### 2023-12-16 manuscript/manuscript.qmd
Use new Ma et al citekey

Similar to recent work by @BaBerrettCoupet:2021 and @Ma-etal:2021 and @Rohrer:2018, in this paper, we provide a introductory primer / framework for approaching causal questions with observational data - accessible and approachable guide to nonprofit researchers and practitioners. The framework here is crucial for general academic research, policy analysis, and program evaluation, among other common types of nonprofit research.

>>>>

Similar to recent work by @BaBerrettCoupet:2021 and @MaEbeiddeWit:2023 and @Rohrer:2018, in this paper, we provide a introductory primer / framework for approaching causal questions with observational data - accessible and approachable guide to nonprofit researchers and practitioners. The framework here is crucial for general academic research, policy analysis, and program evaluation, among other common types of nonprofit research.
